\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{tikz-timing}
\usepackage[table,dvipsnames]{xcolor}
\usepackage{cleveref}
\crefname{figure}{Fig.}{Figs.}
\Crefname{figure}{Fig.}{Figs.}
\crefname{table}{TABLE}{TABLES}
\Crefname{table}{TABLE}{TABLES}
\crefname{equation}{}{}
\Crefname{equation}{Equation}{Equations}
\usepackage{svg}
\usepackage{subfig}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\graphicspath{{../figures/}}
\input{../definitions/timingsetup.tex}
\begin{document}

\title{Memristor-based recurrent modules for neural computing}


\author{\IEEEauthorblockN{Valentin BARBAZA}
%\IEEEauthorblockA{\textit{Master student} \\
%\textit{name of organization (of Aff.)}\\
Lisbon, Portugal \\
valentin@barbaza.org}


\maketitle

\begin{abstract}
  In this work we propose an analog structure for memristor based recurrent modules targeting neural computing. The system is fully analog and implements a working \ac{LSTM} circuit block and a work in progress \ac{GRU} circuit block. Both of those blocks contain memristors to be used as weights in a analog \ac{VMM} capable circuit. These circuit blocks allow to run very fast computation of \aclp{RNNs} of any size, in a relatively small integrated circuit. As part of the \ac{LSTM} and \ac{GRU} blocks, an analog activation function circuit was designed. This specific circuit is capable of reproducing sigmoid and \ac{tanh} like functions, with similar shapes and the same output ranges. The work also include the implementation of a memory cell used to store an analog value for a short period of time. The \ac{LSTM} block can be serialized or not with the ability to choose the level of serialization. Serializing the system allows to save onChip area at the cost of execution time. To the author's knwoledge this is the first analog implementation of the behavior of \acs{C. elegans} using the \ac{LSTM} block. Such an analog system provides ground for real time implementation of nervous systems.
\end{abstract}

\begin{IEEEkeywords}
  Memristors, Crossbar array, VMM, Machine Learning, RNN, LSTM, GRU, Analog computing, Analog circuits, Analog activation functions, Tensorflow, Keras, Embedded systems, Neural computing
\end{IEEEkeywords}

\section{Introduction}

AIs (Artificial Intelligences) are one of the main research domain in computer sciences and is used in other scientific domains. One great application of AI, is in embedded systems. Lots of small electronic devices around us could benefit us. \textbf{Google} and \textbf{Apple} are pushing AI in phones with their in house designed ARM processors having, very advertised, tensor cores.
Being able to run low powered AIs is thus one of the biggest computer objective of the deceny.
Analog computers are known to be a low powered technology that most importantly give almost instant results. An analog ASIC (Application Specific Integrated Circuit) could then be fabricated for specific embedded applications. This would definitely improve digital technologies in terms of time, and maybe in power consumption as well, these being two prerequisite for embedded system use.
For this reason this work aims at creating a functioning software simulation of analog circuit capable of running AI. The thesis will focus on the software simulation, the first step of the work in order to have a fully working chip able to run AI algorithms.

\input{state.tex}
\input{circuit.tex}
\input{tools.tex}
\input{dataset.tex}
\input{results.tex}
\input{conclusion.tex}


\bibliographystyle{IEEEtran}
\bibliography{../definitions/biblio}

\end{document}
